\chapter*{List of own publication activities and other outcomes}
\label{sec:ListOfStudentsOwnPublicationActivitiesAndOtherOutcomes}
\addcontentsline{toc}{chapter}{\nameref{sec:ListOfStudentsOwnPublicationActivitiesAndOtherOutcomes}}
\verb|biblatex| can be used to compile a list of own publications and other outputs, whether related or not related to the dissertation. Individual bibliographic records of own publications are marked, in \verb|.bib| file, using keywords such as \verb|OwnRelated | and \verb|OwnNonRelated|. Package \verb|biblatex| allows you to filter individual records based on these keywords.

Adapt the page to individual needs, the formatting example of this page is not binding.

\begin{refsection}
\nocite{MyRelatedArticle1, MyRelatedArticle2}
\printbibliography[keyword={OwnRelated}, heading=subbibintoc, title={Publications and Outcomes Related to Thesis}]
\end{refsection}

\begin{refsection}
\nocite{MyNonrelatedArticle1}
\printbibliography[keyword={OwnNonRelated}, heading=subbibintoc, title={Publications and Outcomes Not Related to Thesis}]
\end{refsection}

\section*{Other Outcomes}
\begin{enumerate}
	\item Specification of outcome A
	\item Specification of outcome B
	\item Specification of outcome C
\end{enumerate}



\chapter*{List of Citations}
\label{sec:ListOfCitations}
\addcontentsline{toc}{chapter}{\nameref{sec:ListOfCitations}}
These non-self citations are known\footnote{Adapt the page to individual needs, the formatting example of this page is not binding.}:
\begin{itemize}
	\item My publication A
		\begin{enumerate}
			\item Other publication citing My publication A
			\item Other publication citing My publication A
			\item etc.
		\end{enumerate}
	\item My publication B
		\begin{enumerate}
			\item Other publication citing My publication B
			\item Other publication citing My publication B
			\item Other publication citing My publication B
			\item etc.
		\end{enumerate}
	\item My publication C
		\begin{enumerate}
			\item Other publication citing My publication C
			\item etc.
		\end{enumerate}
\end{itemize}



\chapter*{List of Projects}
\label{sec:ListOfProjects}
\addcontentsline{toc}{chapter}{\nameref{sec:ListOfProjects}}
During my doctoral studies, I participated in these projects\footnote{Adapt the page to individual needs, the formatting example of this page is not binding.}:
\begin{itemize}
	\item as principal investigator
		\begin{enumerate}
			\item Project A specification
			\item Project B specification
			\item etc.
		\end{enumerate}

	\item as co-investigator
		\begin{enumerate}[resume]
			\item Project C specification
			\item etc.
		\end{enumerate}

	\item as team member
		\begin{enumerate}[resume]
			\item Project D specification
			\item etc.
		\end{enumerate}
\end{itemize}

\endinput